Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-04-16 papers/B1555_EdgeOn/B1555_letter.tex
Edits to modeling section of B1555 paper

\begin{figure*}
%\begin{minipage}{140mm}
%\includegraphics[width=140mm]{B1555_gallery.eps}
\includegraphics[width=0.95\textwidth]{B1555_gallery.eps}
\caption{High-resolution multiband imaging of the B1555+375 lens system.
All of the panels are 3\farcs7 on a side, and for each panel the scale bar 
represents 1\arcsec.  From left to right the figures show data from
HST/WFPC2 in the F555W band, HST/WFPC2 in the F814W band, HST/NICMOS/NIC2
in the F160W band, and Keck AO imaging in the $K^\prime$ band.}
%
%\end{minipage}

@@

The B1555+375 system was also observed by the Hubble Space Telescope
(HST) in three broad bands.  The optical data were obtained with the
Wide-Field Planetary Camera 2 (WFPC2) in the F555W and F814W bands
(GO-8804; PI: E.\ Falco), while the Near Infrared Multi-Object
Spectrograph (NICMOS) was used to observe the system in the $F160W$
band (GO-9744; PI: C.\ Kochanek).  The NICMOS observations were
obtained with the NIC2 camera.  We reduced all of the archival HST
data with the standard {\tt multidrizzle} pipeline [?? CHECK WITH
MATT], producing final drizzled images with pixel scales of
50~mas.  The reduced images are shown in Figure~??.  The lens system
is not detected at high significance in the optical bands, but is
clearly seen in the NICMOS $F160W$ image.  The edge-on lensing galaxy 
stands out in the NICMOS image.

@@

To model B1555+375, we use the lens modelling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image positions
and flux densities measured by the radio observations of \citet{Marlow}.
These authors present a singular isothermal ellipsoid (SIE) model that
provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A and B.
(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In $K^\prime$ band
imaging (Fig. 1, left), a recognizable edge-on disk is lie in the center
with position angle $\approx 10$ degree. The detection of edge-on disk also explain the missing images B \& D in near-infrared (Fig 1, right). Image B \& D very likely are extincted by the edge-on disk since the images have the same orientation with the disk.

By adding a disk component, we apply our new discover from AO image to the
B1555+375 modelling. The first model consists of an SIE bulge
and an exponential edge-on disk (SIE+expdisk). And the second model
consists of two SIE mass profiles (2-SIE), for bulge and disk
respectively. We assume that the lens galaxy has $z_{l}=0.5$ and the source has $z_s=1.5$. The full best-fit parameters are shown in Table 2. Both
of these models predict fairly matched results with the radio
observation, and the 2-SIE model has a better performance in flux ratios. The comparison of observation and our lens modelling is
in Figure 3, Table 3 \& 4.

\begin{figure}
%\plotone{1555_ao_merlin_overlay.eps}
\includegraphics[width=84mm]{1555_ao_merlin_overlay.eps}
\caption{High-resolution  $K^\prime$ band imaging of the B1555+375 lens system with MERLIN radio observation overlaid.
%
\label{fig:merlin}}
\end{figure}

>>>>

\begin{figure*}
%\begin{minipage}{140mm}
%\includegraphics[width=140mm]{B1555_gallery.eps}
\includegraphics[width=0.95\textwidth]{B1555_gallery.eps}
\caption{High-resolution multiband imaging of the B1555+375 lens system.
All of the panels are 3\farcs7 on a side, and for each panel the scale bar 
represents 1\arcsec.  From left to right the figures show data from
HST/WFPC2 in the F555W band, HST/WFPC2 in the F814W band, HST/NICMOS/NIC2
in the F160W band, and Keck AO imaging in the $K^\prime$ band.
\label{fig:multiband}}
%
%\end{minipage}

@@

The B1555+375 system was also observed by the Hubble Space Telescope
(HST) in three broad bands.  The optical data were obtained with the
Wide-Field Planetary Camera 2 (WFPC2) in the F555W and F814W bands
(GO-8804; PI: E.\ Falco), while the Near Infrared Multi-Object
Spectrograph (NICMOS) was used to observe the system in the $F160W$
band (GO-9744; PI: C.\ Kochanek).  The NICMOS observations were
obtained with the NIC2 camera.  We reduced all of the archival HST
data with the standard {\tt multidrizzle} pipeline [?? CHECK WITH
  MATT], producing final drizzled images with pixel scales of 50~mas.
The reduced images are shown in Figure~\ref{fig:multiband}.  The lens
system is not detected at high significance in the optical bands, but
is clearly seen in the NICMOS $F160W$ image.  The edge-on lensing
galaxy stands out in the NICMOS image.

@@

To model B1555+375, we use the lens modeling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image
positions and flux densities measured by the radio observations of
\citet{Marlow}.  These authors present a singular isothermal ellipsoid
(SIE) model that provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A
and B.  \citep[see Fig.~6 and Tables 2 \& 3 in][]{Marlow}.  Although
the flux ratio anomaly that is observed in the radio data may be
caused by substructure in the lensing galaxy, our high-resolution near
infrared imaging suggests another explanation.  In both the $K^\prime$
band adaptive optics data and the HST imaging (two rightmost panels in
Fig. 1), the lensing galaxy has a clear edge-on disk component with a
position angle of $\approx 10$ degree.  We therefore model the system
with a disk component in order to see if such a model can explain the
flux ratio anomaly without the need for substructure.  The edge on
disk may also explain the system morphology that is observed in the
near infrared imaging.  In particular, neither image B nor image D is
detected in the Keck AO data (Fig.~\ref{fig:merlin}), and both of
these lensed images lie on or close to the edge-on disk.  Thus, strong
extinction in the disk could cause the lack of detection of these
images.

We have created two separate models of the lensing potential.  In the
first we treat the lens as a SIE bulge and an exponential edge-on disk
(SIE+expdisk).  In the second model the disk is represented as a very
elongated SIE component (2-SIE).  The lens system is red, with a
strong jump in flux between the F814W (roughly I) and F160W (roughly
H) bands (Fig.~\ref{fig:multiband}), so we assign a lens redshift of
$z_\ell = 1.0$ and a source redshift of $z_s =$?? [{\bf WHAT VALUE DID
    WE USE??}].  The full best-fit parameters are shown in Table
2. Both of these models predict fairly matched results with the radio
observation, and the 2-SIE model has a better performance in flux
ratios. The comparison of observation and our lens modelling is given
in Figure 3 and Tables 3 \& 4.

\begin{figure}
%\plotone{1555_ao_merlin_overlay.eps}
\includegraphics[width=84mm]{1555_ao_merlin_overlay.eps}
\caption{High-resolution  $K^\prime$ band imaging of the B1555+375 lens system 
with contours from the MERLIN observation of \citet{Marlow} overlaid.
%
\label{fig:merlin}}
\end{figure}
